Matrix Transposition and Symmetry: a case study on Superscalar Architectures\\

### 2024-11-29 latex/paper.tex
report: experiments and system description draft

- Detailed description of the computing system and platform. \\
- Relevant specifications or configurations (e.g., libraries
and programming toolchains). \\
- Description of the experimental setup, procedures, and
methodologies used in the project. \\
- Discussion on how experiments are designed to test the hypotheses
or achieve the objectives \\

The experiments were conducted on a cluster equipped with 64 x86\_64 cpus, more specifically Intel(R) Xeon(R) Gold 5220 CPU @ 2.20GHz.

>>>>

\iffalse
- Detailed description of the computing system and platform. \\
- Relevant specifications or configurations (e.g., libraries
and programming toolchains). \\
- Description of the experimental setup, procedures, and
methodologies used in the project. \\
- Discussion on how experiments are designed to test the hypotheses
or achieve the objectives \\
\fi

The experiments were conducted on a cluster equipped with 64 Intel(R) Xeon(R) Gold 5220 CPUs at 2.20GHz, 32K of L1d cache, 32K L1i cache, 1025K L2 cache, 25344K L3 cache with cache lines of 64 bits, 1 thread per core, 4GB of DDR4 RAM running Linux 3.10.
The algorithms were benchmarked using valFuzz \ref{b?}. The set of benchmarks were compiled with flags "-fopenmp", "-fopenmp-simd", 4 set of benchmarks are compiles with either no optimizations, -O1, -O2, -O3 -Ofast -march=native.
To obtain results with statistical significance, each benchmark has been executed 100 times collecting the following data concerning wall-clock execution time: minimum, maximum, median, arithmetic mean, standard deviation, Q1, Q3.
To prevent interference between the benchmarks, the cache is cleared by initializing an array twice as big as the L3 cache size.
To ensure fair comparison, the same input matrix is provided to all algorithms.
The input matrix is initialized with an uniform random distribution of floats ranging from -1 to 1 generated using lcg algorithm \ref{b?} with the parameters a=1664525 and c = 1013904223.
To save time, generation of random numbers is done at compile time using tenno-tl \ref{b?} with the initial seed "1337". Additional algorithms and data structures were used from tenno-tl including ranges and arrays.
